\documentclass[11pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{fontawesome}
\usepackage{enumitem}
\DeclareFontFamily{U}{fontawesomeOne}{}
\DeclareFontShape{U}{fontawesomeOne}{m}{n}
{<-> FontAwesome--fontawesomeone}{}
\DeclareRobustCommand\FAone{\fontencoding{U}\fontfamily{fontawesomeOne}\selectfont}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{#1}}%
     \item[]
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
{\setlength{\leftmargin}{-0.5#1}}%
\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
#1 &
#2 \\
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
	{\LARGE \textbf{Wasim Akhtar}}\\
	Greater Noida, India
	\vspace{0.05cm}
	\\
	\raisebox{-0.2\height} {\Large \faPhoneSquare} \ \  9718742936 \hfill\raisebox{-0.2\height}{\Large \faEnvelopeSquare} \ \ wasim.akh2@gmail.com \hfill \raisebox{-0.2\height}{\Large \faGithubSquare} \ \ /wasimakh2 \hfill \raisebox{-0.2\height}{\Large \faLinkedinSquare} \ \ linkedin.com/in/wasim-akhtar-3b7436b
\end{center}

\hrule
\vspace{-1em}
\subsection*{\Large Experience}

\renewcommand\labelitemi{}
\renewcommand\labelitemii{$\bullet$}
\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
		
	\item
	      \headerrow
	      {\textbf{Concentrix Daksh Service PVT LTD}}
	      {\textbf{Gurgaon, IN}}
	      \headerrow
	      {\emph{Software Engineer III}}
	      {\emph{June 2015 -- Present ( Includes 1 Year on Artech Payroll )}}
	      \begin{itemize*}
	      	\item Developing and Deploy Enterprise .NET Application WPF,WebAPI,AWS Lambda,Azure Serveless Function.
	      	\item Analysis on problems and provide a solution.
	      	\item Managing and Leading Internal Automation Team Projects
	      \end{itemize*}
	      \headerrow
	      {\emph{Software Engineer II}}
	      {\emph{June 2014 -- October 2016}}
	      \begin{itemize*}
	      	\item Implemented critical detail page and globalized item publishing features to help launch the \emph{Rest of World} project, which enabled customers from 200+ countries to purchase digital software and video games.
	      	\item Designed and implemented an automated accounting solution for the Digital Software \& Video Games business, reducing the work required in monthly accounting close from 10+ hours to 2 hours.
	      	\item Created an internal Django website for vendor managers to manage pricing, blacklisting, and inventory for software and video games, reducing monthly operational time spent from 20+ hours to 10 hours.
	      \end{itemize*}
	      	      
	\item
	      \headerrow
	      {\textbf{Jabong.com}}
	      {\textbf{Gurgaon, IN}}
	      \headerrow
	      {\emph{Mis Executive}}
	      {\emph{October 2014 -- June 2015}}
	      \begin{itemize*}
	      	\item Creating Macros for Process
	      	\item Analysis on problem and automation
	      	\item Generating Report on Daily, Weekly and Monthly basis for PO and Item codes.
	      \end{itemize*}
	\item
	      \headerrow
	      {\textbf{Concentrix Daksh Service PVT LTD}}
	      {\textbf{Gurgaon, IN}}
	      \headerrow
	      {\emph{SR. PRACTITIONAR}}
	      {\emph{Nov 2012 -- October 2014}}
	      \begin{itemize*}
	      	\item Generating Report on Daily, Weekly and Monthly basis for Quality \$Saving by Automated Audit Tool. 
	      	\item Managing data using Excel VBA.
	      \end{itemize*}
	      	      
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Skills}

\hyphenpenalty=1000
\begin{itemize}[leftmargin=1em,noitemsep]
	\item \textbf{Languages:}
	      C\#, HTML/CSS, JavaScript, Python, SQL
	\item \textbf{Software:}
	      Atlassian (Bitbucket, Jira, Confluence), AWS (DynamoDB, EC2, Lambda, RDS, Redshift, S3, SQS), Microsoft (Azure DevOps, Visual Studio),  Django, Heroku, Selenium
\end{itemize}

\hrule
\vspace{-1em}
\subsection*{\Large Education}

\begin{itemize}[leftmargin=1em]
	\parskip=0.1em
		
	\item
	      \headerrow
	      {\textbf{IGNOU}}
	      {\textbf{PATNA , IN}}
	      \headerrow
	      {\emph{B.C.A Bachelor of Computer Application} (\textbf{Grade:} A)}
	      {\emph{July 2017 -- Dec 2010}}
	\item
	      \headerrow
	      {\textbf{BIHAR BOARD}}
	      {\textbf{Bettiah , IN}}
	      \headerrow
	      {\emph{12th MATHEMATICS AND SCIENCE} (\textbf{Division:} Second)}
	      {\emph{2006 -- 2007}}
	      \headerrow
	      {\emph{Matriculation MATHEMATICS AND SCIENCE} (\textbf{Division:} First)}
	      {\emph{2005 -- 2005}}
\end{itemize}

\end{document}
